|

### 2020-08-04 paper.Rmd
figure tweaks

```{r density, fig.cap="Histogram of two-dimensional projections of 10k points sampled uniformly within a $p$-dimensional hyperspheres, for $p=3, 10, 100$. The fill color shows the logarithm of the bin count, with the highest counts shown in yellow. As $p$ increases the samples concentrate near the center.", out.width="95%", fig.align = "center"}

@@

ggplot(proj_points, aes(x, y)) +
  geom_hex(bins = 20, aes(fill=log(..count..))) +
  scale_fill_viridis_c() +
  theme_bw() +
  facet_wrap(~p, scales = "free") +
  guides(fill = FALSE) +
  theme(axis.title.x=element_blank(), axis.title.y=element_blank(), aspect.ratio = 1)

>>>>

```{r density, fig.cap="Histogram of two-dimensional projections of 10k points sampled uniformly within a $p$-dimensional hyperspheres, for $p=3, 10, 100$. The fill color shows the logarithm of the bin count, with the highest counts shown in yellow. As $p$ increases the samples concentrate near the center.", out.width="95%", fig.width=6, fig.height=2, fig.align = "center"}

@@

ggplot(proj_points, aes(x, y)) +
  geom_hex(bins = 20, aes(fill=log(..count..))) +
  scale_fill_viridis_c() +
  theme_bw() +
  facet_wrap(~p, scales = "free") +
  guides(fill = FALSE) +
  theme_void() + 
  theme(#axis.title.x=element_blank(), 
        #axis.title.y=element_blank(), 
        aspect.ratio = 1)
